Coordinated shifts in allocation among reproductive tissues across 14 coexisting plant species

### 2017-12-06 ms/Accessory/Wenk-Accessory-SI.Rnw
Changes to Accessory paper
Updating figures for RA and adding SuppMatt
- added lat & lon to site file by converting from UTM coordinates (closes #31)
- added maps of filed sites
- reformatted suppmat style (it broke)

print_table_species <- function(species, data) {
  data <- data[data$Species == species, -c(1)]
  print(xtable(data,
            hline.after=c(1),
            align='p{0.1cm}p{4.5cm}p{6cm}p{2cm}p{1cm}p{1cm}',
            label=sprintf("tab:parts_%s", gsub(" ", "_", species)),
            caption=sprintf("Table of parts for \\emph{%s}.", species)),
      sanitize.text.function=I,
      , table.placement = "h"
      , caption.placement = "top"
      , include.rownames = FALSE
      , include.colnames = TRUE
      , size = "small"
      , tabular.environment = 'longtable'
      , floating = FALSE)
}

print_table_metadata <- function(path, align = NULL) {

  data <-  read.csv(path, stringsAsFactors=FALSE, check.names=FALSE)
  file <- gsub("_", "\\_", basename(path), fixed = TRUE)

  label <- sprintf("tab:%s_meta", strsplit(basename(path), "_")[[1]][1])

  print(xtable(data,
            align=align,
            hline.after=c(1),
            label= label,
            caption=
              sprintf("Description of variables within the file \\texttt{data/%s}. These definitions can also be found within the file \\texttt{data/%s}.",
              gsub("\\_meta", "", file, fixed = TRUE), file)),
      , table.placement = "h"
      , caption.placement = "top"
      , include.rownames = FALSE
      , include.colnames = TRUE
      , size = "small"
      , tabular.environment = 'longtable'
      , floating = FALSE)
}
@

@@

\begin{table}[H]
\centering
\caption{Testing for shifts in accessory costs with in age, plant size, or reproductive effort. Shifts in accessory costs with these variables is suggested as one possible explanation of increasing reproductive investment in larger, older plants, but such a trend did not exist in these data.}
\label{tab:access_vs_age}
\begin{tabular}{p{4cm}|x{.75cm}x{1cm}x{1.25cm}|x{.75cm}x{1cm}p{1.25cm}|x{.75cm}x{1cm}p{1.25cm}}
\hline
& \multicolumn{3}{c|}{Accessory costs} & \multicolumn{3}{c|}{Accessory costs}& \multicolumn{3}{c}{Accessory costs} \\
& \multicolumn{3}{c|}{vs. RE} & \multicolumn{3}{c|}{vs. plant mass}& \multicolumn{3}{c}{vs. age} \\
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS16)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as 'flower weight $\times$ bud count'. Due to the high proportion of aborted flowers, flower investment was a better proxy of reproductive investment than was propagule investment. This was true both across species (Figure 3, Table 3 in the main text) and within species, as is shown here.}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{4cm}|x{.75cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
\hline
& \multicolumn{3}{c|}{Total reproductive investment} & \multicolumn{3}{c}{Total reproductive investment} \\
& \multicolumn{3}{c|}{vs. propagule investment} & \multicolumn{3}{c}{vs. flower investment} \\
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS17)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

@
\begin{table}[H]
\centering
\caption{Scaling of reproductive tissue costs with total propagule size. In this manuscript all "seed size" calculations use embryo and endosperm size, not propagule size. Most previous research has used propagule size as a measure of "seed size" and noted isometric relationships between various tissue costs and "seed size". Using embryo and endosperm size, these relationship did not exist for this data set, but are present if "seed size" includes the entire propagule.}
\label{tab:repro_tissues_vs_prop_size}
\begin{tabular}{p{5cm}|x{.75cm}x{3.5cm}p{3cm}}
\hline
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS19)
         , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

We collected data for 14 species (Table \ref{tab:species}) at 7 sites (Tables \ref{tab:sites}). Individuals were selected as described in the main text.

<<echo=FALSE,results='asis'>>=
  data <-  read.csv("../../data/species.csv", stringsAsFactors=FALSE, check.names=FALSE)
  data$Common_name <- firstup(data$Common_name)
  names(data) <-  clean_headers(names(data))

  print(xtable(data,
            align= 'p{1cm}p{5cm}p{3cm}p{3cm}p{2cm}p{3cm}',
            hline.after=c(1),
            label= "tab:species",
            caption="Details on study species."),
      , table.placement = "h"
      , caption.placement = "top"
      , include.rownames = FALSE
      , include.colnames = TRUE
      , size = "small"
      , tabular.environment = 'longtable'
      , floating = FALSE)

@@

  print(xtable(data,
            align= 'p{0.1cm}p{2cm}p{1cm}p{1cm}p{1cm}p{1.4cm}p{1.4cm}p{7cm}',
            hline.after=c(1),
            label= "tab:sites",
            caption="Details on study sites."),
      , table.placement = "h"
      , caption.placement = "top"
      , include.rownames = FALSE
      , include.colnames = TRUE
      , size = "small"
      , tabular.environment = 'longtable'
      , floating = FALSE)
@

>>>>

@

@@

\begin{table}[h]
\centering
\caption{Testing for shifts in accessory costs with in age, plant size, or reproductive effort. Shifts in accessory costs with these variables is suggested as one possible explanation of increasing reproductive investment in larger, older plants, but such a trend did not exist in these data.}
\label{tab:access_vs_age}
\begin{tabular}{p{4cm}|x{.75cm}x{1cm}x{1.25cm}|x{.75cm}x{1cm}p{1.25cm}|x{.75cm}x{1cm}p{1.25cm}}
\hline
& \multicolumn{3}{c|}{Accessory costs} & \multicolumn{3}{c|}{Accessory costs}& \multicolumn{3}{c}{Accessory costs} \\
& \multicolumn{3}{c|}{vs. RE} & \multicolumn{3}{c|}{vs. plant mass}& \multicolumn{3}{c}{vs. age} \\
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS16)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

\begin{table}[h]
\centering
\caption{Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as 'flower weight $\times$ bud count'. Due to the high proportion of aborted flowers, flower investment was a better proxy of reproductive investment than was propagule investment. This was true both across species (Figure 3, Table 3 in the main text) and within species, as is shown here.}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{4cm}|x{.75cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
\hline
& \multicolumn{3}{c|}{Total reproductive investment} & \multicolumn{3}{c}{Total reproductive investment} \\
& \multicolumn{3}{c|}{vs. propagule investment} & \multicolumn{3}{c}{vs. flower investment} \\
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS17)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

@
\begin{table}[h]
\centering
\caption{Scaling of reproductive tissue costs with total propagule size. In this manuscript all "seed size" calculations use embryo and endosperm size, not propagule size. Most previous research has used propagule size as a measure of "seed size" and noted isometric relationships between various tissue costs and "seed size". Using embryo and endosperm size, these relationship did not exist for this data set, but are present if "seed size" includes the entire propagule.}
\label{tab:repro_tissues_vs_prop_size}
\begin{tabular}{p{5cm}|x{.75cm}x{3.5cm}p{3cm}}
\hline
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS19)
         , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

We collected data for 14 species (Table \ref{tab:species}) at 7 sites (Tables \ref{tab:sites}, Fig. \ref{fig:map}). Individuals were selected as described in the main text.

<<echo=FALSE,results='asis'>>=

data <-  read.csv("../../data/species.csv", stringsAsFactors=FALSE, check.names=FALSE)
data$Common_name <- firstup(data$Common_name)
i <- data$Previous_names != ""
data$Species_name[i] <- sprintf("%s (previously %s)", data$Species_name[i],data$Previous_names[i])
data <- dplyr::select(data,-Previous_names)

names(data) <-  clean_headers(names(data))

print(xtable(data,
          align= 'p{1cm}p{5cm}p{3cm}p{5cm}p{2cm}',
          hline.after=c(1),
          label= "tab:species",
          caption="Details on study species."),
    , table.placement = "h"
    , caption.placement = "top"
    , include.rownames = FALSE
    , include.colnames = TRUE
    , size = "small"
    , tabular.environment = 'longtable'
    , floating = FALSE)

@@

print(xtable(data,
          align= 'p{0.1cm}p{2cm}p{1cm}p{1cm}p{1cm}p{1.2cm}p{1.2cm}p{1.2cm}p{1.2cm}p{5cm}',
          hline.after=c(1),
          digits=c(0,0,0,2,0,0,0,4,4,0),
          label= "tab:sites",
          caption="Details on study sites."),
    , table.placement = "h"
    , caption.placement = "top"
    , include.rownames = FALSE
    , include.colnames = TRUE
    , size = "small"
    , tabular.environment = 'longtable'
    , floating = FALSE)
@

\begin{figure}[h]
\centering
\includegraphics[height=10cm]{../map.pdf}
\caption{Map of study locations.}
\label{fig:map}
\end{figure}
